\section{Implementation}

\subsection{Overview}
This section explains the current implementation of the developed tool set, it
is primarily targeted to fulfill the dissertation's requirements. But is also
aiming to be helpful for users wanting to understand the underlying systems and
prepare them for potentially joining the development effort. Abridged code
extracts are used as of their state for thesis submission, while the main
principles will hold, later readers are asked to please consult the actual
source code if any discrepancies arise. First the main libraries are shortly
explained in their relevance to the program, second the largely abstract plugin
architecture is shown, third the main plugins are presented and last the
delivery processes to the end users are described.


All implementation files are contained and delivered inside a single git
repository, which is freely available online:
\url{https://github.com/ksjogo/oxrti}. All following file paths are relative to that repository's root. All future development will
be immediately available there and the current compiled software version is
always fed automatically from it into the hosted version at \url{https://oxrtimaster.azurewebsites.net/api/azurestatic}.

\subsection{Libraries}
\begin{description}
\item[TypeScript:]  The official header line of TypeScript show some points why
  it was picked for this project: ``TypeScript is a typed superset of JavaScript that compiles
  to plain JavaScript. Any browser. Any host. Any OS\@. Open
  source.''\cite{noauthor_typescript_2018} Which fits
  requirements~\ref{req_os},~\ref{req_system}. Whereas plain JavaScript would
  have allowed slightly easier initial on-boarding and maybe easier immediate
  code `hacks', TypeScript will provide better stability in the long run and a
  quite improved developer experience (requirement~\ref{req_dx}) in the long
  run. With the full typed hook system (compare \autoref{sec_hooks}) it ensures
  that a compiled plugin will not have runtime type problems, reducing the
  amount of switching between code editor and the running software. The whole
  project is setup in a way to fully embrace editor tooling, Visual Studio
  Code\cite *{noauthor_visual_nodate} and Emacs\cite*{noauthor_gnu_nodate} are
  the `officially' tested editors of the project. Code is recommended as it will
  support all developer features out of the box. The installation of the
  tslint\cite*{noauthor_tslint_nodate} plugin\cite*{noauthor_tslint_nodate-1} is
  recommended to keep a consistent code style, which is configured within the
  \emph{tslint.json} file.
\item[React]\todoT{React}
\item[mobx]\todoT{mobx}
\item[mobx-state-tree]\todoT{mobx-state-tree}
\item[gl-react]\todoT{gl-react}
\item[webpack]\todoT{webpack}\cite{renaudeau_gl-react_2018}
\item[electron]\todoT{electron}
\item[misc]\todoT{misc}\cite{noauthor_mobx:_2018}
\end{description}

\subsection{Plugin architectures}
\todoT{Plugin architectures}

\begin{typescript}
  function murks() : number{}
\end{typescript}

\subsection{Hooks}\label{sec_hooks}

\input{fileformats}


\subsection{Loader}


\subsection{State Management}
\todoT{state management}
\todoT{state import/export}
\todoD{redux}
\todoD{mobx actions}

\subsection{Components}
\todoT{single component units}

\subsection{Renderer Stack}
\todoT{base rendering nodes}
\todoD{stacked components}
\todoD{effects}

\subsection{Plugins}
\todoT{Plugins API}
\subsubsection{Converter Plugin}
\todoT{Converter Plugin}
\subsubsection{PTMConverter Plugin}
\todoT{PTMConverter Plugin}
\subsubsection{Renderer Plugin}
\todoT{Renderer Plugin}
\todoT{Base Node}
\todoT{WebGL texture packing}
\subsubsection{PTM Renderer Plugin}
\todoT{PTM Renderer Plugin}
\todoT{Dynamic Shaders}
\todoT{RGB vs LRGB}
\subsubsection{Light Control Plugin}
\todoT{Light Control Plugin}
\subsubsection{Rotation Plugin}
\todoT{Rotation Plugin}
\subsubsection{Zoom Plugin}
\todoT{Zoom Plugin}
\subsubsection{QuickPan Plugin}
\todoT{Zoom Plugin}
\subsubsection{Paint Plugin}
\todoT{Zoom Plugin}
\subsubsection{Import Export Plugin }
\todoT{Automatic Import Export}

\subsection{Applications}
\todoT{Other related graphics}
\todoT{Applications}
\subsubsection{Standalone Website}
\todoT{Standalone Website}
\subsubsection{Embeddable}
\todoT{Embeddable}
\subsubsection{Electron}
\todoT{Electron App deliverable}
