\section{Requirements and Design}
\subsection{Requirements}
I arrived at the following functional requirements, which are
logically grouped into fileformat/support and viewer.

For the fileformat:
\begin{enumerate}
\item Support for the PTM\cite*{library_of_congress_polynomial_2018}  fileformat.
\item Support for the RTI\cite*{library_of_congress_reflectance_2018} fileformat.
\item Conversion of the formats above into a unified format.
\item Extended metadata support.
\item Support for high resolutions.
\item Support for higher bitdepths per pixel than the 8 of PTM/RTI.
\item Easy exchange between multiple researchers.
\end{enumerate}

For the viewer component:
\begin{enumerate}[resume]
\item Compatible with all major operating systems and/or web browsers.\label{req_system}
\item Lightening Controls.
\item Quick navigation functionality.
\item Annotations.
\item Overlays.
\end{enumerate}

These non-functional requirements were extracted:
\begin{enumerate}[resume]
\item  Free Software, the implementation should be available for everyone to
  change and distribute. \label{req_os}
\item Suitable of new developers: for scientists for research purposes,
  or students for educational purposes. \label{req_easy}
\item Good developer experience. \label{req_dx}
\item Adequate performance, at least keeping up with current
  implementations. \label{req_performance}
\item Easy installation for
  researchers. \label{req_install}
\item ``Web''-Based.
\item Fast responses to user interactions. \label{req_react}
\item Reasonable file sizes for instant transfer/viewing.
\item Preservable software and BTF files.\label{req_preserve}
\end{enumerate}

\subsection{Fileformat}
Though the LoC deems the PTM format ``''relatively transparent. It can be viewed
in plain text editors. [\ldots] A very simple program would present these
numbers in a human-readable
form.''\cite*{library_of_congress_polynomial_2018} the author disagrees with
this judgment.


\subsection{State-Driven}
\todoT{State-Driven}
\subsection{Plugins}
\todoT{Plugins}
\subsection{Rendering Stack}
\todoT{Rendering Stack}

\subsection{Workflow}
\todoD{Workflow comparison}json
\todoT{File import/export}

\subsection{Fileformat}

\subsection{Novelties}
\todoT{Novelties Design}